Working with negative binomial regression

### 2021-12-30 text/21/negative-binomial-regression.Rmd
Fixed typos in tags

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: "New"
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear models
output: html_document
---

>>>>

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: "New"
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
output: html_document
---
